Why do we Eval?\\[2mm]\Large A large-scale study of Eval usage in R

### 2020-12-17 analysis/usage.Rmd
progress

overview_table(
  r("median size eval", med_size),
  r("max size eval", max_size),
  r("average size eval", average_size),
  r("size nine five", nb_nodes_many$arg_size),
  r("size nine five exact percent", percent(nb_nodes_many$cumulative))
) -> TBL

@@

```{r amount_computations, include=F}
tot_events <- E %>% summarise(n=sum(opcodes)) %>% .$n
max_events <- E %>% summarize(max = max(opcodes)) %>% .$n

>>>>

overview_table(
  r("Medianszeval", med_size),
  r("Maxszeval", max_size),
  r("Avgszeval", average_size),
  r("Szninefive", nb_nodes_many$arg_size)
  ) -> TBL

@@

```{r amount_computations, include=F}
tot_events <- E %>% summarise(n=sum(opcodes)) %>% .$n
max_events <- E %>% summarize(n = max(opcodes)) %>% .$n

### 2020-12-17 paper/main.tex
progress

To provide a picture of \eval usage in R, we recorded \Allcalls
invocations of \eval and its variants in the CRAN corpus. These calls
were obtained by \Nbruns runs, with runs that did not trigger \eval
discarded. Out of the \Staticatleastonecallsite CRAN packages(among
the \Corpus packages of our corpus) with \eval call sites, we observed
calls in \Triggeredpkgs packages, the difference can be chalk down to
incomplete code coverage and occasional failures due to our pipeline.

@@

\mypara{Amount of code loaded by eval.} We use \c{deparse} to turn the
input to \eval into strings and measure the size of that input. The
largest input is \MaxSizeEval and the median input size is
\MedianSizeEval. Most inputs are small, less than \SizeNineFiveRnd
bytes. The average size is \AverageSizeEval bytes.

>>>>

To provide a picture of \eval usage in R, this section focuses on
library code and the \Corpus packages in the CRAN corpus. Data was
collected from \Nbruns runs of code extracted from the target packages
and their reverse dependencies. In total, \Allcalls invocations of
\eval and its variants were recorded. Runs that did not call \eval
were discarded.\footnote{The fact that a package contains call sites
to \eval does not mean every run will execute those call sites.} Out
of the \Staticatleastonecallsite packages that use \eval,
\Triggeredpkgs packages we recorded calling the function --- the
difference can be chalk down to incomplete code coverage and
occasional failures in our pipeline.

@@

\mypara{Amount of code loaded by eval.} We use \c{deparse} to turn the
input to \eval into strings and measure the size of that input. The
largest input is \Maxszeval and the median input size is
\Medianszeval. Most inputs are small, less than \SzninefiveRnd
bytes. The average size is \Avgszeval bytes.
